\chapter{Characteristics}

\section{Absolute maximum ratings}
Stresses that exceed the limits specified in this section may cause permanent damage to the device. 
Proper operation of the device within the limits specified in this section is not implied.  

\begin{ZubaxTableWrapper}{Absolute maximum ratings}
    \begin{ZubaxWrappedTable}{| X | c | c | c |}
    Parameter                 & Min   & Max    & Unit           \\
    Supply voltage            & -0.3  & 36     &   V            \\
    Phase current amplitude   &       & 45     &   A            \\
    DC continuous current     &       & 30     &   A            \\
    Operating temperature     & -40   & 85     &   \degree{}C   \\
    CAN H/L input voltage     & -0.3  & 7      &   V            \\
\end{ZubaxWrappedTable}
\end{ZubaxTableWrapper}

\section{Electrical characteristics}

\begin{ZubaxTableWrapper}{Electrical characteristics}
    \begin{ZubaxWrappedTable}{| X | c  c  c | c |}
    Parameter                               & Min   & Typ   & Max   & Unit            \\
    Supply voltage                          & 12    &       & 33.6    & V               \\
    Idle current consumption                & 3     &       & 10    & mA              \\
    FET drain-source on-state resistance    &       & 6     &       & $\text{m}\Omega$\\
    Inverter temperature measurement range  & -55   &       & 125   & \degree{}C      \\
    Inverter temperature measurement error  & -6    &       & 6     & \degree{}C      \\
    Motor temperature measurement range     & -55   &       & 150   & \degree{}C      \\
    Motor temperature measurement error     & -5    &       & 5     & \degree{}C      \\
\end{ZubaxWrappedTable}
\end{ZubaxTableWrapper}

\section{Environmental conditions}

\begin{ZubaxTableWrapper}{Environmental conditions}
    \begin{ZubaxWrappedTable}{| l | X | c  c | c |}
    Parameter                   & Note                       & Min & Max    & Unit          \\
    Operating temperature       &                            & -40 & 85     & \degree{}C    \\
    Storage temperature         &                            & -40 & 50     & \degree{}C    \\
    Operating humidity          & Condensation not permitted & 0   & 100    & \%RH          \\
    Operating altitude          & Above mean sea level (MSL) &     & 10     & km            \\
\end{ZubaxWrappedTable}
\end{ZubaxTableWrapper}

\section{Operational characteristics}

\begin{ZubaxTableWrapper}{Power characteristics}
\begin{ZubaxWrappedTable}{| l | X | X | c |}
    Parameter                           & Sadulli Piccino   & Sadulli Grosso    & Unit  \\
    Continuous power                    & 500               & 500               &   W   \\
    Peak power (30sec)                  & 700               & 700               &   W   \\
    Thrust in efficient mode\tnote{a}   & 700               & 1500              &   gf  \\
    Max thrust                          & 1500              & 4000              &   gf  \\
\end{ZubaxWrappedTable}
\begin{tablenotes}
\item [a] - The efficient mode is the mode where the device produces not less than 10 gf of thrust per each watt of electrical power consumed
\end{tablenotes}
\end{ZubaxTableWrapper}

\begin{ZubaxTableWrapper}{Characteristics of CAN bus interfaces}
    \begin{ZubaxWrappedTable}{| X |c c c | c |}
        Parameter                                 & Min  & Typ  & Max  & Unit               \\
        Bit rate                                  & 20   &      & 1000 & Kbps               \\
        Positive-going input threshold voltage    &      & 750  & 900  & mV                 \\
        Negative-going input threshold voltage    & 500  & 600  &      & mV                 \\
        Differential output voltage, dominant     & 1.5  & 2.0  & 3.0  & V                  \\
        Differential output voltage, recessive    & -120 & 0    & 12   & mV                 \\
        Bus power rail voltage                    & -10  &      & 10   & V                  \\
        Inter-connector current                   & -1   &      & 1    & A                  \\
        Connector resistance during device lifetime &    & 30   & 50   & $\text{m}\Omega$   \\
    \end{ZubaxWrappedTable}
\end{ZubaxTableWrapper}

\begin{ZubaxTableWrapper}{BEC characteristics}
\begin{ZubaxWrappedTable}{| X | l | c |}
    Parameter            & Value   & Unit               \\
    Output voltage       &  4.9    & V                  \\
    Voltage tolerance    &   2     & \%                 \\
    Maximum load current &  500    & mA                 \\
    Voltage ripple       &  100    & m$V_\text{p-p}$    \\
\end{ZubaxWrappedTable}
\end{ZubaxTableWrapper}

\subsection{Regenerative braking}
During regenerative braking, the device performs energy transfer from the motor to the power supply network. 
If the self-resistance of the power supply network is not sufficiently low, 
the regenerative energy transfer may lead to an increase of the supply voltage beyond the safe operating limits. 
Generally, batteries are capable of absorbing the energy recovered during braking without issues. 
Problems may arise if the device is powered from a source that does not permit high reverse currents, 
such as laboratory power supplies. 
In that case, it is advised to install additional buffer capacitors to act as energy storage during braking.

\subsection{Power connectors}
Zubax Sadulli is equipped with an XT30PW-M power connector. 
The mating XT30U-F connector may be provided as connector only or as a connector with pre-soldered 100 mm 16 AWG wires.

\section{CAN bus}

The device is equipped with a single ISO 11898-2 CAN 2.0A/B interface. 
CAN interface has two standard UAVCAN Micro connectors\footnote{Refer to \url{http://uavcan.org} 
for more information on UAVCAN.} joined in parallel. 
The device does not terminate the CAN bus internally.

\begin{ZubaxSimpleTable}{CAN bus connectors pinout}{| c | X | X | }
    Pin no. & Type         & Name   \\   
    1       & Power        & PWR    \\  
    2       & Input/Output & CAN H  \\  
    3       & Input/Output & CAN L  \\  
    4       & Ground       & GND    \\
\end{ZubaxSimpleTable}

\section{BEC output}
Zubax Sadulli features software-controllable BEC output. It is available on bus power supply pin of UAVCAN connectors. 
BEC output is protected against short circuit, maximum output current is 500 mA.  
It is also protected against the reverse current flow with an ideal diode. 

