\chapter{Indication}

\newcommand{\LEDX}{{\rule{0.4em}{1.0em}}}
\newcommand{\LEDO}{{\rule{0.4em}{0.1em}}}
\newcommand{\ShowColor}[1]{{\color{#1}\rule{2em}{0.8em}}}

Zubax Sadulli is equipped with two separate LED indicators that reflect its status.

\textbf{CAN} green LED indicates data transfer through the CAN bus.
Blinks once if at least one CAN frame was successfully transmitted or successfully received in the last 25 milliseconds.
Glows steadily when the intensity of CAN traffic is higher than 40 frames per second.

\textbf{STATUS} RGB LED indicates the status of the firmware.
The behaviour of the status LED is specified in the table below.

\begin{ZubaxSimpleTable}{Status LED during boot}{|l l X|}
             Color              & Status                              & Description                                      \\
    \ShowColor{yellow} Yellow   & No application to boot              & The firmware has not been flashed to the ESC
                                                                        or FLASH has been damaged.                       \\
    \ShowColor{blue} Blue       & Application upgrade is in progress  &                                                  \\
    \ShowColor{green} Green     & Boot canceled                       & The device firmware has not been properly signed.\\
    \ShowColor{magenta} Magenta & Ready to boot                       & Glows after the device power-up or restart event
                                                                        until the application starts.                    \\
\end{ZubaxSimpleTable}

\begin{ZubaxSimpleTable}{Status LED behavior}{|l X X|}
    LED pattern (step 80 ms)                     & Status                    & Description \\

    {\color{blue}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX}           & Idle, ready to run        & The ESC is ready and waiting for the
                                                                               setpoint. \\
    
    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDX\LEDX} & Idle, hardware fault      & The power stage is not ready or current
                                                                               is tripped. \\

    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDO\LEDX\LEDX\LEDX}
                                                 & Idle, hardware test fault & The motor is not connected or there is a
                                                                               short circuit on the output of the
                                                                               ESC. \\

    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDX\LEDX\LEDO\LEDX
       \LEDX\LEDX}                          & Idle, invalid motor parameters & Some motor parameters are not properly
                                                                               initialized or the motor identification
                                                                               hasn't been performed. \\
\end{ZubaxSimpleTable}

